### 2015-06-29 Manuscript/BiologyLetters/Missing_mammals-draft.tex
Updated morphobank typo

%---------------------------------------------
%
%       METHODS
%
%---------------------------------------------
\section{Materials and Methods}
\subsection{Data collection and standardisation}
We downloaded all cladistic matrices containing any living and/or fossil mammal taxa from three major public databases: Morphobank (\url{http://www.morphobank.org/} \cite{morphobank}), Graeme Lloyd's website (\url{graemetlloyd.com/matrmamm.html}) and Ross Mounce's GitHub repository (\url{https://github.com/rossmounce/cladistic-data}).
We also performed a systematic Google Scholar search for matrices that were not uploaded to these databases (see Supplementary Materials Section 1 for a detailed description of the search procedure).
In total, we downloaded 286 matrices containing 5228 unique operational taxonomic units (OTUs). 
We used OTUs rather than species since entries in the matrices ranged from species to families, and standardised the taxonomy as described in Supplementary Materials (section 1). 
We designated as ``living'' all OTUs that were either present in the phylogeny of \cite{BinindaEmonds} or the taxonomy of \cite{wilson2005mammal}.

>>>>

%---------------------------------------------
%
%       METHODS
%
%---------------------------------------------
\section{Materials and Methods}
\subsection{Data collection and standardisation}
We downloaded all cladistic matrices containing any living and/or fossil mammal taxa from three major public databases: MorphoBank (\url{http://www.morphobank.org/} \cite{morphobank}), Graeme Lloyd's website (\url{graemetlloyd.com/matrmamm.html}) and Ross Mounce's GitHub repository (\url{https://github.com/rossmounce/cladistic-data}).
We also performed a systematic Google Scholar search for matrices that were not uploaded to these databases (see Supplementary Materials Section 1 for a detailed description of the search procedure).
In total, we downloaded 286 matrices containing 5228 unique operational taxonomic units (OTUs). 
We used OTUs rather than species since entries in the matrices ranged from species to families, and standardised the taxonomy as described in Supplementary Materials (section 1). 
We designated as ``living'' all OTUs that were either present in the phylogeny of \cite{BinindaEmonds} or the taxonomy of \cite{wilson2005mammal}.
